---
title: "Tidal Culvert Data Status"
output: 
  flexdashboard::flex_dashboard:
    storyboard: false
    theme: spacelab
    source: embed
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
source("00_libraries.R")
knitr::read_chunk("code/rmdSetup.R") # read code chunks from external files to extend beyond multiple Rmds.
```

```{r directorySetup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
```

```{r spatialDataLoad, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
```

```{r culvertData, message=FALSE, warning=FALSE, paged.print=FALSE}
```

Identifying Crossings {data-width=1200}   
===========================================  

Column{data-width=800}    
-------------------------------------------  

These are _*ALL*_ points that have been flagged as potential tidal culverts.  

The map below contains all the cuvlerts that have been identified and that are currently in the Long Island Culvert Mapping group on AGOL. These data also house the desktop data as extracted from the Workbooks in late September. The data are being updated direct to the AGOL dataset.  

Crossings are colored by 'Status'    

```{r allPtsMap, fig.height=5, fig.show='hold', fig.width=12, message=FALSE, warning=FALSE, paged.print=FALSE}
# Crossings that have been IDed via ArcMap and from partners.
# TODO: Tidal stations - check windy API
# TODO: Add popups and/or labels on hover. 

LIculvertMap <- mapview(LIculvertDataStatus_location, 
                               zcol = 'FieldAssessmentComplete', 
                               label = as.character(LIculvertDataStatus_location$crossingID), lwd = .5,
                               cex = 4, legend = TRUE, layer.name = "Tidal Crossings:<br> Assessment Status")
LIculvertMap 

```


Column{data-width=400}
------------------------------------------- 

Status of assessments.   

```{r fieldassessmentVisits, message=FALSE, warning=FALSE, paged.print=FALSE}

LIculvertDataStatus_location %>% st_drop_geometry() %>% 
  group_by(FieldAssessmentComplete,listedOnFieldSched) %>%
  summarise(n=n()) %>% spread(key = listedOnFieldSched, value = n) %>% 
  rename("Priority" = "TRUE", "Non-priority" = "FALSE") %>% 
  kable()
# 
LIculvertDataStatus_location %>% st_drop_geometry() %>% 
  select(FieldAssessmentComplete, listedOnFieldSched) %>%
  rpivotTable(rows = "FieldAssessmentComplete", cols = "listedOnFieldSched", rendererName = "Heatmap")

  
  
```


Missing bits... 
===========================================  

Column{data-width=400}  
------------------------------------------- 

Desktop Assessment  
  

```{r out.width='100%', message=FALSE, warning=FALSE, paged.print=FALSE}
LIculvertData_location %>% select(crossingID, starts_with("da_"), -ends_with("Comts")) %>% 
  st_drop_geometry() %>% 
  plot_missing(ggtheme = theme_ipsum()) %>% plotly::ggplotly()
```

Column{data-width=800}  
-------------------------------------------   

## Desktop Data -missing-by-crossing- 

Proportion of desktop assessment data missing from dataset.

  
```{r out.width='100%', message=FALSE, warning=FALSE, paged.print=FALSE}

LIculvertDataStatus_location %>% 
  select(crossingID, 
         # select the desktop assessment fields
         starts_with("da_"), 
         
         # do not select the NWI classifications as many are missing and not collected.
         -starts_with("da_NW"), 
         
         # do no select the comments fields
         ends_with("Comts")) %>% 
  
  # Calculate the proportion of desktop assessment variables that are missing.
  mutate(propNa = rowMeans(is.na(.), na.rm = T)) %>% 
  
  # Select just the calculated proportion and the crossingID for mapping.
  select(crossingID, propNa) %>% 
  mapview(cex = "propNa", na.color = 'red', zcol = "propNa", layer.name = "Proportion NA's")


```



Culvert height measures {data-width=1200}
===========================================  

Column{data-width=800}  
-------------------------------------------

Proportion of crossings that have a measure for each feature and position (up/down stream)  

```{r}
# Pivot Table
hwi_qunat <- LIculvertsAssessments %>% select(crossingID, heights) %>%  
  unnest() %>% mutate(hasHt = !is.na(adjustedHt) | !is.na(Height))

crosComs <-   LIculvertData %>% select(crossingID, crossSection_hts_coms) %>% mutate(crossingID = as.character(crossingID))
  
hwi_qunat %>% filter(hasHt == TRUE) %>% select(crossingID, Feature, Position) %>% 
  left_join(crosComs) %>% rpivotTable(rows = "crossingID", cols = c("Feature", "Position"), rendererName = "Heatmap", aggregatorName = "Count")

hwi_qunat %>% filter(hasHt == TRUE) %>% select(crossingID, Feature, Position) %>% 
  group_by(crossingID, Feature, Position) %>%
  tally() %>% 
  unite(col = "FeaturePos", sep = "  -  ", Feature, Position) %>% 
  spread(key = FeaturePos, value = n) %>% 
  left_join(crosComs) %>% 
  write_xlsx(path = "Y:/CrossSectionalCompleteness.xlsx")



```

Column{data-width=400}  
-------------------------------------------
### Distribution of 'Completeness'

```{r message=FALSE, warning=FALSE, paged.print=FALSE}

# crossingTracker %>%
#   group_by(`Field Ass. Complete(Y/N)`) %>% tally()
  
# determine the missing HWI's by crossing
hwi_qunat %>% 
  mutate(crossingID = as.numeric(crossingID)) %>% 
  group_by(crossingID, hasHt) %>%
  filter(hasHt == FALSE) %>%
  tally() %>% mutate(propMissing = n/13) %>% arrange(desc(propMissing)) -> htProps

htProps %>% 
  ggplot(aes(x = propMissing)) + geom_histogram(bins = 30) + theme_ipsum()


```

Culvert height measures - Locations {data-width=1200}
===========================================  

Column{data-width=800}  
-------------------------------------------

### Distribution of 'Completeness'  
Circle color is representative of the % of NA values in the height measures for each crossing.


```{r}
  
# hwi_qunat %>% group_by(crossingID) %>% plot_missing()
# #   
# rpivotTable(hwi_qunat, rows = c("Feature", "Position"), cols = "hasHt", rendererName = "Heatmap", aggregatorName = "Count as Fraction of Rows")
tidalCrossings_desktop %>% left_join(htProps) %>%  mapview(zcol = "propMissing", layer.name = "Proportion of Height Measures")
```

Culvert height measures - High water clearance {data-width=1200}
===========================================  

Column{data-width=800}  
-------------------------------------------

```{r}
# hwi_qunat %>% select(crossingID, Feature, Position, hasHt) %>% spread(Feature, hasHt) %>% group_by(crossingID, Position) %>% mutate(highWat = sum(`Ceiling of Structure`, `HWI Stain`, `HWI Wrack`, `Road Surface`, na.rm = T)/4) %>% select(crossingID, Position, highWat) %>% filter(!is.na(Position)) %>% group_by(Position, highWat) %>% tally()




```
Table of distribution of crossings that have 

