---
title: "Tidal Culvert Data QA-QC"
output: 
  rmdformats::html_clean:
    highlight: kate
---
** TOTAL WORK IN PROGRESS **

This attempts to both outline the current status of the tidal culvert data and provide a task list for walking through the data collected to date and the data that are yet to be collected. Sort of a hybrid documentation of methods and to-do list.

```{r knitr_init, echo=TRUE, message=FALSE, warning=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

library(readr)
library(readxl)
library(tidyxl)
library(unpivotr)
library(tidyverse)
library(sf)
library(mapview)
library(rstudio)

tidalCulvert_datasheetsFolder <- "../../Box Sync/Tidal Assessments/Culvert Excel Sheets"
tidalCulvert_outputs <- "../../Box Sync/Tidal Assessments"
keysheet <- read_excel("../../Box Sync/Tidal Assessments/key.xlsx")
culvertPts_path <- "M:/Projects/LI/Culvert_Assessment/data/Tidal Crossings/TidalCrossings_20180712.shp" # Direct path to the shapefile used as base. Change as needed. # UPDATE:
LIculvert_GISpts <- st_read(culvertPts_path)

LIculvert_GISpts <- LIculvert_GISpts %>% mutate(crossingID = as.character(Tidal_ID))

cleanLIculvert_GISpts <- LIculvert_GISpts %>% filter(Latitude != 0)

source("functions/culvert_tidy.R")
source("functions/culvert_extract.R")    
```



```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}


LIculvertsAssessments <- culvert_tidy(tidalCulvert_datasheetsFolder) %>% 
  mutate(decoded = map(.x = tidycells, .f = ~decodeSheet(.x, keysheet))) # this is where the sausage is made. 


# unnest the tidyxl data to create a large tidy dataframe
LIculvertData <- LIculvertsAssessments %>% 
  select(filenames, decoded) %>% 
  unnest() %>% select(filenames, dataName, values) %>% 
  spread(key = dataName, value = values) %>% 
  select(filenames, crossingID, dateAssessed, observers, everything()) # organize the order of the columns.



if(typeof(LIculvertData$crossingID) == typeof(LIculvert_GISpts$crossingID)){ # Are the two columns the same datatype?
  matchedLIculverts <- LIculvertData %>% filter(crossingID %in% LIculvert_GISpts$crossingID) %>% select(filenames, crossingID)
  missingLIculverts <- LIculvertData %>% filter(!crossingID %in% LIculvert_GISpts$crossingID) %>% select(filenames, crossingID)
}


```

## Output 
Here's the output-- 
I added an option to the table so that a local version can be saved- It's a bit clumbsy here since it's so wide (lots of variables) but you can scroll left/right to see all the columns- or click 'Download' to save a copy to open in Excel.
 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
DT::datatable(LIculvertData, rownames = FALSE, 
              extensions = 'Buttons', 
              options = list(
    dom = 'Bfrtip',
    buttons =
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'
      ))
  )
  )

xlsx::write.xlsx(LIculvertData, file = paste0(tidalCulvert_outputs, "/compiledTidalData.xlsx"))

```


## Missing Spatial Data by CrossingID
The following list contains filenames of datasheets that *DO NOT* have a corresponding location in shapefile (path: `r culvertPts_path `).  
Just a note that currently the only linkage between the field data sheets and the spatial data (the locations for culverts as derived from remotely sensed and groundtruthed data) are the CrossingID field. Care must be taken to ensure the names are entered correctly.  

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
DT::datatable(missingLIculverts, rownames = FALSE, 
              extensions = 'Buttons', 
              options = list(
    dom = 'Bfrtip',
    buttons =
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'
      ))
  )
  )



```


## Mapped Culverts
Out of the pile of datasheets in the folder _(`r tidalCulvert_datasheetsFolder`)_ this map shows locations that have a corresponding datasheet. 
The map below are locations (though some inaccuracies are evident...) of culverts with a related 'field datasheet' info. Click a point to see details. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

LIculvertData_location <- cleanLIculvert_GISpts %>% right_join(LIculvertData, by = "crossingID") # this object is picking up 2 extra joins- perhaps dupicate CrossingIDs?
map_assessedLItidalCulverts <- mapview(LIculvertData_location, zcol = "Assessed", cex = 4)
map_assessedLItidalCulverts

# TODO: Add that marsh complex priority shapefile that was used for the ebird work.
```

### Locations that have spatial data but no corredsponding data sheets. 

Color coded by 'Priority'


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

map_missingsDataPts <- mapview(cleanLIculvert_GISpts %>% filter(!crossingID %in% LIculvertData$crossingID), zcol = 'Priority', cex = 4)

map_missingsDataPts

```



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# citations <- function(includeURL = TRUE, includeRStudio = TRUE) {
#     if(includeRStudio == TRUE) {
#         ref.rstudio <- RStudio.Version()$citation
#         if(includeURL == FALSE) {
#             ref.rstudio$url = NULL;
#         }
#         print(ref.rstudio, style = 'text')
#         cat('\n')
#     }
#
#     cit.list <- c('base', names(sessionInfo()$otherPkgs))
#     for(i in 1:length(cit.list)) {
#         ref <- citation(cit.list[i])
#         if(includeURL == FALSE) {
#             ref$url = NULL;
#         }
#         print(ref, style = 'text')
#         cat('\n')
#     }
# }
#
# citations()
```



