---
title: "Tidal Crossing Score Summary <img id=\"tnc-logo.svg\" src=\"tnc-logo.svg\" />"
date: "`r Sys.Date()`"
output: 
  pagedown::poster_jacobs:
  self_contained: false
css: summary_v2.css
params:
  crossingCode: 441

---

```{r setup, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
# TODO: make sure to insert references and cite r packages
# htmltools::includeScript(path = here::here("script.js"))
# insert 
# insert- knit: pagedown::chrome_print in the yml above to print direct to pdf


```

```{=html}
<script src="//ajax.googleapis.com/ajax/libs/jquery/1.10.1/jquery.min.js"></script>
```
```{r dataload, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Add ->  knit: pagedown::chrome_print
# to save as pdf while knitring
source(here::here("00_libraries.R"), local = knitr::knit_global())
source(here::here("summarySheetSetup.R"), local = knitr::knit_global())

ccode = params$crossingCode

# TODO: Move 'structure condition' to the proper section.

# TODO: ADD THE RELEVENT TIDAL DATA HERE
# Prioritization data
tidalPrioritization <- read_rds(here::here("data", "/LIculvertPrioritizations.rds")) %>% filter(crossingID == ccode) 
# Full Assessment data
tidalAssessmentData <- read_rds(here::here("data", "/LIculvertAssessmentData.rds")) %>% filter(crossingID == ccode)
# Profiles plots (created in rmdSetup.Rmd to shave time on rendering summary sheets.)
profilePlot <- read_rds(here::here("data", "/LIculvertAssessments.rds")) %>% 
  filter(crossingID == ccode) %>% pull(profilePlots)


tsdn <- read_rds(here::here("data", "/tsdn.rds")) # crosswalk table for building out the summary sheet tables
# TODO: Add in the info such as structure material etc. Determine if that should be done here or elsewhere in the line (perhaps in the tidalPrioritization call?)
# Data that's needed for summary sheet but not in prioritization data.
# - Plot data for longitudinal profiles.
# - anxillary data such as number of local crossings inundated by SLR
slrScenarios <- read_rds(here::here("data/slrScenariosLOOKUP.rds")) # for lookups below. 
photoLookup <- read_xlsx(here::here("summarySheets/photomatchTable_tidal.xlsx")) # photos will likely need to be local to ensure they render in htmls.
photoFolder <- here::here("summarySheets", "tidal_photos")



# IDEA: 1st step: filter, select the proper columns needed for the summary sheet, with column identifying the section that it will land. 
# 2nd step: filter crossing of interest from larger dataset, transpose the data to be in long format and then join to above data frame. 
# 3rd step: For each chunk of the summary sheet, filter based on section and then make table using kable or gt or other.

# filter crossing of interest
tidal_doc_data <- tidalPrioritization %>% 
  filter(crossingID == ccode) 

# Pull coords for use in general summary section
coords <- tidal_doc_data %>% st_coordinates() %>% 
  as_tibble() %>% rename(longitude = X, latitude = Y) %>% mutate(latitude = paste0("N ", as.character(round(latitude, digits = 3))), 
                                                                 longitude = paste0("W ", as.character(round(longitude, digits = 3))))



tidal_doc_data <- tidal_doc_data %>% left_join({tidalAssessmentData %>% st_drop_geometry()})


tidal_table_data <- tidal_doc_data %>%
  mutate(
    # make a character string of the coordinates for text section.
    Coordinates = paste(
      round(st_coordinates(.)[2], digits = 5),
      "N ",
      round(st_coordinates(.)[1], digits = 5),
      "W",
      sep = ""
    ),
    # lots of recoding values into human readable text. Most of which is used in the tables within the summary sheet.
    CrossingType = recode(
      CrossingType,
      `2` =                          "Round Culvert",
      `3`  =                     "Elliptical Culvert",
      `4`  =                      "Pipe Arch Culvert",
      `5`  =                            "Box Culvert",
      `6`  =                 "Embedded Round Culvert",
      `7`  =           "Embedded Elliptical Culvert",
      `8`  =           "Embedded Pipe Arch Culvert",
      `9`  =                       "Open Bottom Arch",
      `10`  =                            "Arch Bridge",
      `11`  =                  "Bridge with Abutments",
      `12`  =                "Bridge with Side Slopes",
      `13`  =  "Bridge with side Slopes and Abutments",
      `14`  =                                  "Other"
    ),
    StructureMaterial = recode(
      StructureMaterial,
      `2`	= 'Concrete',
      `3`	= 'Plastic-Corrugated',
      `4` =	'Plastic-Smooth',
      `5`	= 'Stone',
      `6` =	'Corrugated Steel',
      `7`	= 'Smooth Steel',
      `8`	= 'Corrugated Aluminum',
      `9`	= 'Wood',
      `10` = 'Other'
    ),
    StructureConditionOverall = recode(
      StructureConditionOverall,
      `2` =	'Good',
      `3` = 'Fair',
      `4` =	'Poor'
    )
  ) %>%
  st_drop_geometry() %>% janitor::adorn_rounding(digits = 2) %>%
  mutate(
    Suffolk_2085_HIGHMED_Inund_Freq = recode(
      ss_Suffolk_2085_HIGHMED_Inund_Freq,
      # How often is..inundated 2080s
      `0` = "Open Water",
      `1` = "Inundated at least once every 30 days",
      `2` = "Inundated at least once every 60 days",
      `3` = "Inundated at least once every 90 days",
      `4` = "Inundated by the 10-year storm",
      `5` = "Inundated by the 100-year storm",
      `6` = "Never",
      `7` = "Below the 100-year storm but connected",
      `8` = "Protected by dikes",
      `-99` = "Never",
      .default = "Never",
      .missing = "Never"
    ),
    # HACK: NA still being added to tables.Fixed below.
    Suffolk_InitialCondition_Inund_Freq	= recode(
      ss_Suffolk_InitialCondition_Inund_Freq,
      # present day storm freq
      `0` = "Open Water",
      `1` = "Inundated at least once every 30 days",
      `2` = "Inundated at least once every 60 days",
      `3` = "Inundated at least once every 90 days",
      `4` = "Inundated by the 10-year storm",
      `5` = "Inundated by the 100-year storm",
      `6` = "Beyond the 100-year storm",
      `7` = "Below the 100-year storm but connected",
      `8` = "Protected by dikes",
      `-99` = "Beyond the 100-year storm",
      .default = "Beyond the 100-year storm",
      .missing = "Beyond the 100-year storm"
    ),
    # StrmName = if_else(StrmName == " ", # If not " " (blank) then use name.
    #                    true = "Unidentified",
    #                    false = as.character(StrmName)),
    Rd_EvacRte = if_else(ss_Rd_EvacRte == 1, "Yes", "No"),
    partPrior = if_else(Score_partPrior == 1, "No", "Yes"),
    da_catchmentLndCover_imperv = paste0(da_catchmentLndCover_imperv, " %"),
    # Are out tidal crossings impervious the same metric as the fresh?
    Functional_Class = recode(
      ss_Functional_Class,
      `-99` = "Undefined",
      `11` = "Principal Arterial - Interstate",
      `12` = "Principal Arterial - Other Freeway/Expressway",
      `14` = "Principal Arterial - Other",
      `16` = "Minor Arterial",
      `17` = "Major Collector",
      `18` = "Minor Collector",
      `19` = "Local"
    ),
    #TODO: Add in formerly connected 
    # Impact on vegetation community
    Vegchoice = case_when(
      formerlyConnected == 1 ~ "Formerly connected/Severe", # First up test if it's a formerly connected...Then proceed with the vegchoice.
                      Vegchoice == "1A" ~ "None", # 1, # native only, same both sides
                      Vegchoice == "2A" ~ "None", # invasives through out, same both sides
                      Vegchoice == "2B" ~ "Slight", #2, # invasives through out, up and down stream communtites are slightly different
                      Vegchoice == "1B" ~ "Moderate", #3, # native only, different species on either side but appear similar (high marsh - low marsh)
                      Vegchoice == "3A" ~ "Moderate", # 3, # invasives on one side, tidal marsh on both sides
                      Vegchoice == "2C" ~ "Severe",  #4, # invasives through out, up and down stream communities represent different marsh types
                      Vegchoice == "3B" ~ "Severe",  #4, # invasives on one side, similar species/marsh type on either side
                      Vegchoice == "3C" ~ "Very Severe",  #5 # invasices on one side, up and down stream different species
                      Vegchoice == "1C" ~ "Very Severe"),   #5, # native only, tidal species one side, fresh species the other.) 
    marshComplex = recode(Score_MarshComplex,
                          '1' = "No marsh", # TODO: Better term needed
                          '3' = " $\\lt 15$ acres", 
                          '5' = "$\\geq 15$ acres"),
    crossingID = as.character(crossingID),
    aopDesc = recode(Score_dotr, 
                     `1` = "None",
                     `2` = "Slight",
                     `3` = "Moderate", 
                     `4` = "Severe",
                     `5` = "Very Severe")
  ) %>%
  tidyr::gather(key = "field_Name", value = "dataValue") %>%
  dplyr::right_join(tsdn) %>% # join in the tidal data that's of interest from the lookup on Teams.
  replace_na(replace = list(dataValue = "  ", score = "--")) %>%
  mutate(score = ifelse(dataType == "score",
                        yes = TRUE,
                        no = FALSE)) %>%
  dplyr::select(Description, dataValue, SummarySection, position, dataType)  %>%
  spread(dataType, dataValue) %>%
  dplyr::select(Description, SummarySection, position, value, score) %>%
  mutate(score = na_if(score,-99)) %>% # pesky -99's sneaking in.
  replace_na(replace = list(value = "--", score = "--")) %>%
  mutate(value = recode(value,
                        `-99` = "--",
                        .default = value))

# Control the order of the values in the tables.
# Edit the summaryNeeds source document on Teams to adjust.
ords <- summaryNeeds %>% 
  filter(protocol == "Tidal", !is.na(Description), !is.na(tableOrder)) %>% 
  select(Description, tableOrder)

# Style for kable tables.
style <- function(.tab, pos = "center"){
  kable_styling(kable_input = .tab, 
                bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = T, 
                position = pos) #%>% 
  # column_spec(1, width = "30em") %>%
    # column_spec(2, width = "10em") 
}

assesDate <- format(tidalAssessmentData$dateAssessed, format = "%B %d, %Y") 
```

# Project Background

The Long Island Road-Stream and Tidal Crossing Improvement Project, led by The Nature Conservancy with input from state, county, municipal, and other partners, has identified and prioritized road-stream and tidal crossings in Suffolk County, NY for upgrade or replacement. The prioritization is based on social and ecological criteria for road-stream crossings, including culverts and bridges, which are an essential element of our transportation network. These crossings allow roads to pass over rivers, streams, tidal creeks, and wetlands. Undersized, poorly designed, or failing infrastructure at these crossings restricts water flow and can lead to road flooding, property damage, degraded natural systems and impaired water quality. Tidal systems need to experience the full tidal signal both to function today and to respond to sea level rise. This document provides prioritization scoring for the tidal crossing described below. Tidal crossings were assessed using the field and desktop methodology developed by The Nature Conservancy in NH, NH Department of Environmental Services, and the University of NH with modifications to make them suitable for NY. With this information, communities can strategically plan capital investments, secure funding, and implement high priority improvement projects with partners.

#### *Prioritization Scoring*

Crossings are prioritized based on four categories of benefits: ecological benefit, resilience benefit, transportation benefit, and infrastructure condition benefit. Within each category, individual metrics are scored on a scale of 1 to 5. Higher scores indicate a greater benefit and therefore higher priority for upgrade or replacement. Within each benefit category, metrics are summed and then re-scaled to 1 to 5. Finally, all four benefit scores are summed to calculate the Total Prioritization Score, with a potential range of 4 to 20. A detailed explanation of all the metrics and scoring methods for this prioritization is provided in the Tidal Prioritization Scoring Summary document found at the [project resources site.](https://tnc.box.com/s/b8blt0go96hlsxu6cb06e9y952scpjfr)

# General Crossing Information

<center>

Assessed on <b>`r assesDate` </b>\
following the:\
**TNC Tidal Protocol**

</center>

```{r CrossingGeneralInfo, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tidal_table_data %>% 
  filter(SummarySection == "Crossing General Information") %>% 
  left_join(ords) %>% 
  arrange(tableOrder) %>% 
  select(Description, value) %>% 
  kable(col.names = NULL) %>% 
  style()

```

# Site Location

<!-- #### `r coords` -->

```{r siteMap, echo=FALSE, fig.align='center', fig.height=1.5, fig.width=2.5, message=FALSE, warning=FALSE, out.width='100%', paged.print=FALSE}

towns <- st_read(here::here("data/basemap_data.gpkg"), layer =  'admin_LI_town_lines', quiet = TRUE)
li <- st_read(here::here("data/basemap_data.gpkg"), layer = "admin_LI_shore_24k", quiet = TRUE)
county <- st_read(here::here("data/basemap_data.gpkg"), layer = "admin_LI_County_line", quiet = TRUE)

coast <- st_read(here::here("data/ne_10m_coastline.shp"), quiet = T)
# roads <- st_read(here::here("data/ne_10m_roads.shp"), quiet = T)

# osmransport
tm_shape(coast) + 
  tm_lines(lwd = 0.1) +
 tm_shape(li) +
  tm_polygons(col = "white",
              lwd = 0.002,
              border.col = "black") +
 tm_shape(county) +
  tm_lines(lwd = 0.2) +
 tm_shape(towns) +
  tm_lines() +
  tmap_mode(mode = "plot") +
 tm_shape(shp = fw_data) +
  tm_dots(col = "grey", size = .05, alpha = .3) +
 tm_shape(shp = tidal_doc_data, is.master = TRUE) +
  tm_dots(col = "red", size = 0.13) +
  tm_layout(outer.margins=c(.05,0,.05,0),  
            inner.margins=c(0,0,.02,0), asp=0, 
            frame = F)
            

```

This crossing is located within the `r if_else(is.na(tidal_doc_data$Estuary_Name) | tidal_doc_data$Estuary_Name == "NA", "", paste0("<strong>", tidal_doc_data$Estuary_Name, "</strong>", " in the"))` <strong>Town of `r tidal_doc_data$town_name` </strong> at the intersection of `r strong(tidal_doc_data$roadName)` and `r strong(if_else(is.na(tidalAssessmentData$streamName), "an unidentified stream", tidalAssessmentData$streamName))`.\
Coordinates: `r coords`

# Final Scoring

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tidal_table_data %>% dplyr::select(-value) %>% 
  arrange(desc(Description)) %>% 
  filter(SummarySection == "Scoring") %>% 
  left_join(ords) %>% 
  arrange(tableOrder) %>% 
  select(Description, score) %>% 
  kable(col.names = NULL, escape = FALSE) %>% 
  # style() %>% 
  # kable_styling(bootstrap_options = "striped", full_width = F)
  style()

```

# Ecological Benefit

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Style for kable tables.
style_eco <- function(.tab, pos = "center"){
  kable_styling(kable_input = .tab, 
                bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = T, 
                position = pos) #%>% 
  # column_spec(1, width = "30em") %>%
    # column_spec(2, width = "10em") 
}

tidal_table_data %>%
  filter(SummarySection == "Ecological Factors") %>%
  pivot_longer(cols = c(value, score)) %>%
  unite(pos_score, position, name) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = pos_score) %>% 


  # Need to drop '--' and ' ' from columns
  
  left_join(ords) %>%
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>%
  select(Description, 
         # upstream_value, 
         # downstream_value, 
         overall_value, 
         overall_score) %>%
  # replace_na(replace =  list(upstream_value = " ", downstream_value = " ", overall_value = "--", overall_score = "--")) %>% 
  kable(col.names = c("", "", "Score"), align = 'lcc') %>%
  # pack_rows("") %>% 
  style_eco() %>%
  I()


additionalInfo <- tidal_table_data %>%
  filter(SummarySection == "AdditionalInfo") %>%# mutate_at(.vars = vars(value, score), .funs = as.numeric) %>%
  pivot_longer(cols = c(value, score)) %>%
  unite(pos_score, position, name) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = pos_score) %>%

  left_join(ords) %>%
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>%
  select(Description,
         overall_value) %>%
  replace_na(replace =  list(verall_value = "--")) %>% 
  mutate(overall_value = recode(overall_value, "  " = "0"))

```



# Resilience Benefit

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tidal_table_data %>% 
  filter(SummarySection == "Resilience Factors") %>% 
  left_join(ords) %>% 
  arrange(tableOrder) %>% 
  select(Description, value, score) %>%
  kable(col.names = c("", "", "Score"), align = 'lcc') %>% 
  style()

```

# Transportation Benefit

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tidal_table_data %>% 
  filter(SummarySection == "Transportation Factors") %>% 
  left_join(ords) %>% 
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>% 
  select(Description, value, score) %>%
  kable(col.names = c("", "", "Score"), align = 'lcc') %>% 
  style()



```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
h2("Infrastructure Condition Benefit")

tidal_table_data %>%
  filter(SummarySection == "Infrastructure Condition") %>% 
  left_join(ords) %>% 
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>% 
  select(Description, value, score) %>%
  kable(col.names = c("", "", "Score"), align = 'lcc') %>% 
  style()



```

\newpage

# Site Photos

```{r fig.align='center', fig.height=3, fig.show="hold", fig.width=3, message=FALSE, warning=FALSE, out.width="48%", paged.print=FALSE}
# upstream
up <- photo_link(crossingID = ccode, matchTable = photoLookup, subject = "upstream", path = photoFolder, tidal = TRUE) %>% # changed to relative path to see if it fixes the chrome_print
                  photo_check()
inlet <- photo_link(crossingID = ccode, matchTable = photoLookup, subject = "inlet", path = photoFolder, tidal = TRUE) %>% 
                  photo_check()
outlet <- photo_link(crossingID = ccode, matchTable = photoLookup, subject = "outlet", path = photoFolder, tidal = TRUE) %>% 
                  photo_check()
down <- photo_link(crossingID = ccode, matchTable = photoLookup, subject = "downstream", path = photoFolder, tidal = TRUE) %>%
                  photo_check()


pic <- function(img, caption){htmltools::HTML(glue::glue("<div class='image'>
  <img src= '{img}' />
  <p class='caption'>{caption}</p>
</div>"))}


```

# Upstream view from structure

```{r fig.show="hold", message=FALSE, warning=FALSE, out.width="48%", paged.print=FALSE, fig.align='center'}
# 
# htmltools::div(class = "pic",
#                div(
#                  class = "imagecolumn",
#                  pic(up, caption = "Upstream view from structure"),
#                  pic(down, "Downstream view from structure"))
#                )

 up


```

# Downstream view from structure

```{r fig.show="hold", message=FALSE, warning=FALSE, out.width="48%", paged.print=FALSE, fig.align='center'}
down
```

# Downstream view toward structure

```{r fig.show="hold", message=FALSE, warning=FALSE, out.width="48%", paged.print=FALSE, fig.align='center'}
# 
# htmltools::div(class = "pic",
#                div(
#                  class = "imagecolumn",
#                  pic(inlet, caption = "Downstream view toward structure"),
#                  pic(outlet, "Upstream view toward structure"))
#                )
# inlet
# h3("Downstream view toward structure")
# outlet
# h3("Upstream view toward structure")

inlet
```

# Upstream view toward structure

```{r fig.show="hold", message=FALSE, warning=FALSE, out.width="48%", paged.print=FALSE, fig.align='center'}

outlet
```  


<!-- \newpage -->

\pagebreak




# Cross Sectional Profile

```{r profilePlots, fig.height=4, fig.width=8, message=FALSE, warning=FALSE, paged.print=FALSE}
#  This section below was an attempt at finding the quickest method to draw these plots individually. The first method, creates a plot for each crossing at the run of the RmdSetup.R code. It nests the plot as an object(ggplot object) in one of the columns of the nested tibble. The other method (the one that is commented out) ran the plotting on the fly- better for editing and checking in batches, but individually took about 10-15 secs longer per plot to run. 
# TODO: Move this step into the original generation of the plots in the Rmdsetup.r
# source("tidal_longitudinalPlots.R")
# LIculvertAssessments <- read_rds(here::here("data", "/LIculvertAssessments.rds"))
# 
# longitudinalProfile_df <- LIculvertAssessments %>% filter(crossingID == ccode) %>% select(longProfile) %>% unnest(cols = longProfile)
# 
# crossHeight_df <- LIculvertAssessments %>% filter(crossingID == ccode) %>% select(crossSectionProfile) %>% unnest(cols = crossSectionProfile)
# 
# pplot <- drawCrossing(longitudinal = longitudinalProfile_df, crossSectional = crossHeight_df)
# 
pplot <-
  profilePlot[[1]] # Converted to use purrr::possibly which returns either a the result or the 'otherwise'
#  user  system elapsed 
# 46.7     4.6    61.2 

if (is.ggplot(pplot)) {
  # p("This diagram shows a cross section of the crossing based on information collected in the field. The crossing structure is shown in grey, and the stream bed is shown in black.")
  # br()
  pplot
} else{
  h4(glue::glue("Crossing #: {ccode} lacks sufficient data to present a longitudinal plot"))
 
}


```

# Crossing Structure Profile Measurements

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results='asis'}

tidal_table_data %>%
  filter(SummarySection == "Profile Details") %>%# mutate_at(.vars = vars(value, score), .funs = as.numeric) %>%
  pivot_longer(cols = c(value, score)) %>%
  unite(pos_score, position, name) %>%
  mutate(value = as.numeric(value)) %>% 
  # filter(!is.na(value)) %>%
  pivot_wider(names_from = pos_score) %>% 
  
  left_join(ords) %>%
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>%
  select(Description, 
         upstream_value,
         downstream_value) %>%
  replace_na(replace =  list(upstream_value = " -- ", downstream_value = " -- ")) %>%
  kable(col.names = c("", "upstream", "downstream"), align = 'lcc') %>%
  # pack_rows("") %>% 
  style_eco() %>%
  kable_styling(position = "float_left") %>%
  I()


```
All profile measures are in feet relative to NAVD88.

# Degree of Tidal Restriction and Aquactic Organism Passage Components

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 

dtr_subcomponents <- tidal_table_data %>% filter(SummarySection == "Ecological Sub Factors") %>%  pivot_longer(cols = c(value, score)) %>%
  unite(pos_score, position, name) %>%
  mutate(value = as.numeric(value)) %>% 
  # filter(!is.na(value)) %>%
  pivot_wider(names_from = pos_score) %>% 
  
  left_join(ords) %>%
  # filter(!is.na(tableOrder)) %>%
  arrange(tableOrder) %>%
  select(Description, 
         overall_score,
         upstream_value,
         downstream_value) %>%
  replace_na(replace =  list(overall_score = " -- ", overall_value = " -- ", upstream_value = " -- ", downstream_value = " -- ")) %>% # warning that this coerces numerics to characters
  kable(col.names = c("", "score", "upstream", "downstream"), align = 'lcc') %>%
  # pack_rows("") %>% 
  style_eco() %>%
  kable_styling(position = "float_left") %>%
  I()

dtr_subcomponents

```
<br> </br>


**`r additionalInfo$overall_value[1]`%** of the land within the watershed (catchment) is protected from development. Today, there are **`r additionalInfo$overall_value[2]`** building structures upstream at risk of flooding in a 100-yr storm. In future conditions, with 39 inches of sea level rise, **`r additionalInfo$overall_value[3]`** building structures will be at risk of flooding.

# *Data Access*  

-   Access to the data associated with this crossing can be found at the [project resources site](https://tnc.box.com/s/b8blt0go96hlsxu6cb06e9y952scpjfr).

# *Disclaimer*  

This document is a screening tool for prioritizing planning efforts and is not intended to replace a site visit for making engineering or management decisions. Due diligence is required to ensure that all infrastructure and property owners, permitting agencies and project engineers are consulted in advance of project planning. Please note that different entities may own the roadway, crossing infrastructure, water management structures, and the surrounding land. Information presented here represents the best available at the time of the assessment.

</div>
